\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{epsfig,xspace,url}
\usepackage{authblk}


\title{CS 6480: Class discussion summary\\
HA 1.b\\}
\author{Your Name}
\affil{School of Computing, University of Utah}

\begin{document}

\maketitle
\section*{Discussion summary}

\begin{itemize}

\item {\it Summary:} Summarize the class discussion of the papers. Note in
particular anything that came out of the discussion that you missed in your
reading, or that made you change your mind. 

\item {\it Strengths and weaknesses:} Note the consensus
in the class, or your own new insights, regarding the strengths and
weaknesses of the paper(s).

\item {\it Connection with other work:} Describe any connections that were made in
the class discussion to other papers (with citations). (Or connections that you realized
as a result of the class discussion.)

\item {\it Future work:} Briefly describe any possibilities
for future work that came out of the discussion and/or were triggered
in your mind because of the discussion.

\end{itemize}
{
  \small 
  \bibliographystyle{acm}
  \bibliography{biblio}
}

\end{document}
\begin{comment}
WWW is a pretty high rank conference 
	=> more for academic research in the world wide web
	
Weakness for talking about how new commercialized 5G is new 
	=> but is has existed for a while now in asia
	
They bring up how they are looking at 5G in the commercial setting  not just in a lab or controlled environment 

Challenges
	=> 5G broad ecosystem: What do we study? 
	=>  

Broad ecosystem
	=> QoE
	=> But they can't really study anything else because they don't have access to it
	 
	 
Related works
	=> Ignored all of the potential 4G related works 
	
Measurement methodology section  
	=> They didn't do all the measurements on Verizon rather than comparing to others
	=> We "confirm" that Galaxy Samsung doesn't have a bottles neck
		=> But how do we know?? 
	=> Server selection
		=> See where the servers are actually located. we don't know if they go the different CDN nodes
			=> This could have caused the variability 
			=> How is this a measurement of 5G?
		=> Could have considered latency 
	=> More detail
	
The 5G throughput has high variation

Figure 4 is not accurate
	=> The first IP hope is not just the ran
	=> There is a huge IP path gap inbetween
	=> Could ping the first IP address using the Traceroute
		=> The end of the internet tunnel is the first ping 
			=> Gateway to the internet 



	

\end{comment}


























































